Changelog

### 2021-05-24 changelog.tex
Updates from Overleaf

Abacus identifies and quantifies side-channel leakages in a single trace. So it suffers from the problem of code coverage.  That is, Abacus may miss some-channel leakages. I have two choices at that time. First, I can use static analysis methods.

>>>>

Abacus identifies and quantifies side-channel leakages in a single trace. So it suffers from the problem of code coverage.  That is, Abacus misses side-channel leakages in the unexecuted code path. I have a few choices. I can use static analysis (model checking or static program analysis). Although I am interested in the static analysis, I am not a big fan of current static analysis tools, especially for side-channel analysis. There are several papers on static side-channel analysis. But nearly all of them have high false positive rates. My personal experience with Coverity is similar. It is a commercial static program analysis tool but still has plenty of false positives.

On the other hand, there are many successful stories
